KidsAIR: Main analysis

### 2020-11-18 main_analysis_initial.Rmd
major model updates new RMD for final analysis

```{r, eval=TRUE, include=TRUE}
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
```

@@

poisson_results <- glm(lrti_events_total ~ treatment + offset(log_person_time_at_risk), 
                       family = "poisson", data = analysis_data)

@@

library(AER)
dispersiontest(poisson_results, trafo=1) # test indicates poisson model is overdispersed

@@

```{r}
# Mixed model variations

poisson_results <- glmer(lrti_events ~ treatment + child_age + (1 | home:cohort:area), 
                         data = analysis_data, family = poisson(link = "log"), offset = log_person_time_at_risk)
summary(poisson_results)

negbin_results <- glmer.nb(lrti_events ~ treatment + child_age + (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                           data = analysis_data)
summary(negbin_results)

logreg_results <- glmer(lrti_events_di ~ treatment + child_age + (1 | home:cohort:area), 
                        data = analysis_data, family = binomial, offset = log_person_time_at_risk)
summary(logreg_results)
```

>>>>

```{r, eval=TRUE, include=TRUE}
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
library(AER)
library(DHARMa)
```

@@

poisson_results <- glm(lrti_events_total ~ treatment_assigned + offset(log_person_time_at_risk), 
                       family = "poisson", data = analysis_data)

@@

library(AER)
dispersiontest(poisson_results, alternative = "greater") # test indicates poisson model is overdispersed

itt_res <- simulateResiduals(poisson_results)
testDispersion(itt_res, alternative = "less")

@@

```{r}
# Mixed model option for primary model

poisson_results <- glmer(lrti_events_total ~ treatment_assigned + child_age + 
                         (1 | home:cohort:area), 
                         data = analysis_data, family = poisson(link = "log"), 
                         offset = log_person_time_at_risk)
summary(poisson_results)
tidy(poisson_results, conf.int = TRUE)

poisson_simres <- simulateResiduals(poisson_results)
testDispersion(poisson_simres, alternative = "less")
plot(poisson_simres, rank = FALSE, quantreg = TRUE)

negbin_results <- glmer.nb(lrti_events_total ~ treatment_assigned + child_age + 
                           (1 | home:cohort:area) + 
                           offset(log_person_time_at_risk), 
                           data = analysis_data)
summary(negbin_results)
tidy(negbin_results, conf.int = TRUE)

negbin_simres <- simulateResiduals(negbin_results)
testDispersion(negbin_simres, alternative = "less")
plot(negbin_simres, rank = FALSE, quantreg = TRUE)

logreg_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                        child_age + person_time_at_risk +
                        (1 | home:cohort:area),
                        data = analysis_data, family = binomial, nAGQ = 20)
summary(logreg_results)
tidy(logreg_results, conf.int = TRUE)

logreg_simres <- simulateResiduals(logreg_results)
testDispersion(logreg_simres, alternative = "less")
plot(logreg_simres, rank = FALSE, quantreg = TRUE)
```

### 2020-11-18 main_analysis_secondary_models.Rmd
major model updates new RMD for final analysis

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) 
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

analysis_data_outliers <- analysis_data %>% 
  #rownames_to_column() %>% 
  #mutate(filter_outliers = if_else(rowname %in% c(57), 1, 0)) %>% 
  mutate(log_person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 2.33, log_person_time_at_risk)) %>% 
  mutate(person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 72, person_time_at_risk))

@@

itt_res <- simulateResiduals(itt_results)
plot(itt_res, rank = FALSE, quantreg = TRUE)

@@

```{r, echo=TRUE}
# Run primary model and print results
er_results <- glmer.nb(lrti_events_total ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + 
                          (1 | home:cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

@@

```{r, echo=TRUE}
# Run primary model and print results
logreg_results <- glmer(lrti_events_di_total ~ treatment_assigned + child_age + 
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial)
#write_rds(logreg_results, paste0(file_path, "Output/logreg_results.rds"))

@@

## At-risk period across treatment arms
```{r}
at_risk_summary <- analysis_data %>% 
  group_by(treatment_assigned) %>% 
  summarize("Mean at-risk time" = mean(person_time_at_risk, na.rm = TRUE),
            "SD at-risk time" = sd(person_time_at_risk, na.rm = TRUE),
            "Med at-risk time" = median(person_time_at_risk, na.rm = TRUE))
at_risk_summary
```

>>>>

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20) 
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

analysis_data_outliers <- analysis_data %>% 
  #rownames_to_column() %>% 
  #mutate(filter_outliers = if_else(rowname %in% c(57), 1, 0)) %>% 
  mutate(log_person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 2.33, log_person_time_at_risk)) %>% 
  mutate(person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 72, person_time_at_risk),
         lrti_events_total = as.factor(lrti_events_total),
         lrti_events_di_total = as.factor(lrti_events_di_total))

@@

itt_res <- simulateResiduals(itt_results)
testDispersion(itt_res, alternative = "less")
plot(itt_res, rank = FALSE, quantreg = TRUE)

@@

```{r, echo=TRUE}
# Run primary model and print results
er_results <- glmer.nb(lrti_events_total ~ pm_mean_sampling_period_iqr + child_age + 
                          education_3level + residents_smoke + 
                          (1 | cohort:area) + offset(log_person_time_at_risk), 
                          data = analysis_data)
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

@@

```{r, echo=TRUE}
# Run primary model and print results
logreg_results <- glmer(lrti_events_di_total ~ treatment_assigned + child_age + person_time_at_risk +
                        (1 | home:cohort:area),
                        data = analysis_data, family = binomial, nAGQ = 20)
#write_rds(logreg_results, paste0(file_path, "Output/logreg_results.rds"))

summary(logreg_results)

# Run primary model and print results
logreg_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + child_age + 
                        education_3level + residents_smoke + 
                        (1 | cohort:area),
                        data = analysis_data, family = binomial, nAGQ = 20)
#write_rds(logreg_results, paste0(file_path, "Output/logreg_results.rds"))

@@

# At-risk period across treatment arms
```{r}
at_risk_summary <- analysis_data %>% 
  group_by(treatment_assigned) %>% 
  summarize("Mean at-risk time" = mean(person_time_at_risk, na.rm = TRUE),
            "SD at-risk time" = sd(person_time_at_risk, na.rm = TRUE),
            "Med at-risk time" = median(person_time_at_risk, na.rm = TRUE))
at_risk_summary
```
